\documentclass[12pt,a4paper]{article}

% Tiếng Việt
\usepackage[utf8]{inputenc}
\usepackage[T5]{fontenc}
\usepackage[vietnamese]{babel}

\usepackage[table]{xcolor}
\usepackage{tabularx}
\usepackage{array}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage[table]{xcolor}
\usepackage{colortbl}

\definecolor{HeaderGray}{RGB}{220,220,220}
\definecolor{Simple}{RGB}{198,239,206}
\definecolor{Medium}{RGB}{255,242,204}
\definecolor{Complex}{RGB}{244,204,204}

\renewcommand{\arraystretch}{1.3}


% Căn lề
\usepackage[
left=3cm,
right=2cm,
top=2.5cm,
bottom=2.5cm
]{geometry}

% Hình ảnh
\usepackage{graphicx}

% Link
\usepackage{hyperref}

% Khoảng cách dòng
\usepackage{setspace}
\onehalfspacing
\newcommand{\chapter}[1]{
	\clearpage
	\section*{#1}
	\addcontentsline{toc}{section}{#1}
}

\begin{document}
	
	\begin{center}
		{\LARGE\textbf{SCIENTIFIC JOURNAL PUBLICATION TREND TRACKING SYSTEM}}
		
		\vspace{0.5cm}
		
		{\large Group 6}
		
	\end{center}
	
	\vspace{1cm}
	
	\vspace{1cm}
	\chapter{\centering\Large\bfseries I. INTRODUCTION}
	\addcontentsline{toc}{chapter}{I. INTRODUCTION}
	\section{Overview}
	\subsection{Project Information}
	
	\begin{itemize}
		\item Project Name: Scientific Journal Publication Trend Tracking System
		\item Group Name: Group 6
		\item Software Type: Web Application
		\item GitHub Repository:
		
		\url{https://github.com/NguyenNgocBaoTram10/Scientific-Journal-Publication-Trend-Tracking-System}
	\end{itemize}
	
	
	\section{Project Background}
	
	Describe the motivation and background of the project.
	
	\section{Scope}
	
	Describe the scope of the project.
	
	\section{Objectives}
	
	Describe the objectives of the project.
	
	\section{System Requirements}
	
	List the functional and non-functional requirements.
	
	\section{System Design}
	
	Describe the architecture, database design, and diagrams.
	
	\section{Implementation}
	
	Describe technologies, APIs, and key features implemented.
	
	\section{Testing}
	
	Describe test cases and testing results.
	
	\section{Conclusion}
	
	Summarize the project outcomes and future improvements.
	
	
	\subsection{Project team}
	
	\begin{table}[h]
		\centering
		\small
		
		\begin{tabularx}{\textwidth}{
				|>{\raggedright\arraybackslash}p{4cm}
				|>{\centering\arraybackslash}p{2cm}
				|>{\centering\arraybackslash}p{3cm}
				|>{\raggedright\arraybackslash}X|}
			\hline
			
			\rowcolor{gray!25}
			\textbf{Full Name} &
			\textbf{Role} &
			\textbf{Student ID} &
			\textbf{Email} \\
			\hline
			
			Lê Thanh Tú &
			Leader &
			049206004778 &
			tult4778@ut.edu.vn \\
			\hline
			
			Nguyễn Ngọc Bảo Trâm &
			Member &
			082306008015 &
			tramnnb8015@ut.edu.vn \\
			\hline
			
			Lê Thị Huyền Trân &
			Member &
			077306003635 &
			tranlth3635@ut.edu.vn \\
			\hline
			
			Trần Trung Hiếu &
			Member &
			089206008473 &
			hieutt8473@ut.edu.vn \\
			\hline
			
			Trần Văn Học &
			Member &
			&
			hoctv5618@ut.edu.vn \\
			\hline
			
			Nguyễn Đoàn Nhật Quang &
			Member &
			079206010585 &
			quangndn0585@ut.edu.vn \\
			\hline
			
		\end{tabularx}
		
		\caption{Project Team Information}
	\end{table}
	
	\clearpage
	
	\setcounter{section}{1}
	
	\section{Functional Requirements}
	
	\subsection{User Authentication and Authorization}
	\begin{itemize}
		\item Users can register a new account.
		\item Users can log in using a valid username and password.
		\item The system assigns permissions based on user roles.
		\item Administrators can manage user accounts and roles.
	\end{itemize}
	
	\subsection{Research Paper Search}
	\begin{itemize}
		\item Users can search research papers by keyword, author name, or journal name.
		\item The system displays matching publication results.
		\item Users can view detailed publication information.
	\end{itemize}
	
	\subsection{Bookmark Management}
	\begin{itemize}
		\item Users can save research papers to personal bookmarks.
		\item The system prevents duplicate bookmarks.
		\item Users can access bookmarked papers later.
	\end{itemize}
	\subsection{Publication Trend Analysis}
	\begin{itemize}
		\item Users can analyze publication trends based on keywords, topics, authors, or journals.
		\item The system generates trend statistics from publication metadata.
		\item The system visualizes trends using charts and dashboards.
	\end{itemize}
	\subsection{Dashboard Visualization}
	\begin{itemize}
		\item Users can view publication statistics through dashboards.
		\item The dashboard displays publication counts, topic distributions, journal distributions, and growth trends.
	\end{itemize}
	\subsection{Trending Topics}
	\begin{itemize}
		\item Users can view trending research topics.
		\item The system ranks topics according to publication frequency and growth rate.
	\end{itemize}
	\subsection{Topic Following}
	\begin{itemize}
		\item Users can follow research topics of interest.
		\item The system stores followed topics for each user.
		\item Users may follow multiple topics.
	\end{itemize}
	\subsection{Notification Management}
	\begin{itemize}
		\item Users receive notifications related to followed topics.
		\item Notifications include new publications, trend changes, and emerging topics.
		\item Users can view notification details.
	\end{itemize}
	\subsection{Report Generation}
	\begin{itemize}
		\item Users can generate analytical reports based on publication trends.
		\item Reports summarize publication statistics and research trends.
		\item Reports are generated from publication metadata.
	\end{itemize}
	\subsection{System Administration}
	\begin{itemize}
		\item Administrators can manage system operations.
		\item Administrators can manage user accounts.
		\item Administrators can configure academic API sources.
		\item Administrators can synchronize publication metadata from external APIs.
	\end{itemize}
	\subsection{Academic Data Synchronization}
	\begin{itemize}
		\item The system synchronizes publication metadata from external academic APIs.
		\item The system validates retrieved metadata.
		\item The system inserts new records and updates existing records.
		\item The system records synchronization logs and statistics.
	\end{itemize}
	
	
	
	\section{Non-Functional Requirements}
	
	\subsection{Usability}
	The interface is intuitive and accessible for all user types.
	
	\subsection{Performance}
	Search results must be returned within 2 seconds.\\
	The system must support at least 500 concurrent users.
	
	\subsection{Reliability}
	System uptime must be at least 99\% during business hours.\\
	Data must be backed up daily.
	
	\subsection{Security}
	User passwords must be hashed before storage.\\
	Role-based access control must be enforced for all features.
	
	\subsection{Maintainability \& Scalability}
	The system must use a modular architecture for easy maintenance.\\
	New data sources can be added without redesigning the existing system.
	
	\section{Limitations of the Project}
	
	\subsection{Limited Use of Full-Text Data}
	\begin{itemize}
		\item The system only uses publication metadata such as title, abstract, keywords, authors, and publication year.
		\item It does not process full-text content, which limits the depth of analysis and understanding of research papers.
	\end{itemize}
	
	\subsection{Restricted Data Scope}
	\begin{itemize}
		\item The system focuses only on selected research fields (e.g., Computer Science and Artificial Intelligence).
		\item Therefore, it does not fully represent trends across all scientific disciplines.
	\end{itemize}
	
	\subsection{Dependence on External APIs}
	\begin{itemize}
		\item The system relies on external APIs such as Semantic Scholar, OpenAlex, and Crossref.
		\item Any API downtime, structural changes, or request limitations may affect system stability and data collection performance.
	\end{itemize}
	
	\subsection{Simplified Trend Analysis and Update Frequency}
	\begin{itemize}
		\item Trend analysis is mainly based on publication frequency and growth rate.
		\item It does not apply advanced Machine Learning or AI models for prediction.
		\item Data is synchronized periodically (daily or weekly), so real-time trends may not be immediately reflected.
	\end{itemize}
	
	\chapter{\centering\Large\bfseries II. PROJECT MANAGEMENT PLAN}
	\addcontentsline{toc}{chapter}{II. PROJECT MANAGEMENT PLAN}
	\addcontentsline{toc}{chapter}{ II. PROJECT MANAGEMENT PLAN}
	\setcounter{section}{0}
	\setcounter{subsection}{0}
	
	\section{Overview}
	\subsection{Scope and estimation}
	
	\begin{longtable}{|c|p{9cm}|c|c|}
		\hline
		\rowcolor{HeaderGray}
		\textbf{\#} & \textbf{WBS Item} & \textbf{Complexity} & \textbf{Duration (Days)}\\
		\hline
		\endfirsthead
		
		\hline
		\rowcolor{HeaderGray}
		\textbf{\#} & \textbf{WBS Item} & \textbf{Complexity} & \textbf{Duration (Days)}\\
		\hline
		\endhead
		
		\multicolumn{4}{|l|}{\textbf{1. Project Initiation}}\\
		\hline
		1.1 & Define project scope & \cellcolor{Medium} Medium & 1\\
		\hline
		1.2 & Collect and analyze requirements & \cellcolor{Complex} Complex & 2\\
		\hline
		
		\multicolumn{4}{|l|}{\textbf{2. Project Management and Environment Setup}}\\
		\hline
		2.1 & Set up development environment (GitHub, Database, Backend, Frontend) & \cellcolor{Simple} Simple & 1\\
		\hline
		2.2 & Design database (ERD, Database Schema) & \cellcolor{Complex} Complex & 2\\
		\hline
		2.3 & Configure security (JWT, RBAC, Password Hashing) & \cellcolor{Complex} Complex & 2\\
		\hline
		
		\multicolumn{4}{|l|}{\textbf{3. System Design}}\\
		\hline
		3.1 & Design Use Case Diagram and Activity Diagram & \cellcolor{Medium} Medium & 1\\
		\hline
		3.2 & Design Sequence Diagram & \cellcolor{Medium} Medium & 1\\
		\hline
		3.3 & Design DFD and ERD & \cellcolor{Medium} Medium & 1\\
		\hline
		
		\multicolumn{4}{|l|}{\textbf{4. System Development}}\\
		\hline
		4.1 & User Registration and Login & \cellcolor{Medium} Medium & 2\\
		\hline
		4.2 & Search Scientific Publications & \cellcolor{Complex} Complex & 2\\
		\hline
		4.3 & View Publication Details & \cellcolor{Medium} Medium & 1\\
		\hline
		4.4 & Bookmark Management & \cellcolor{Medium} Medium & 1\\
		\hline
		4.5 & Research Topic Following & \cellcolor{Medium} Medium & 1\\
		\hline
		4.6 & Notification Management & \cellcolor{Medium} Medium & 1\\
		\hline
		4.7 & Publication Trend Analysis & \cellcolor{Complex} Complex & 3\\
		\hline
		4.8 & Develop Statistical Dashboard & \cellcolor{Complex} Complex & 2\\
		\hline
		4.9 & Display Trending Topics & \cellcolor{Medium} Medium & 1\\
		\hline
		4.10 & Generate Statistical Reports (PDF/CSV) & \cellcolor{Complex} Complex & 2\\
		\hline
		
		\multicolumn{4}{|l|}{\textbf{5. Administration Functions}}\\
		\hline
		5.1 & User Management & \cellcolor{Complex} Complex & 2\\
		\hline
		5.2 & Configure Academic API Sources & \cellcolor{Complex} Complex & 2\\
		\hline
		5.3 & Synchronize Data from Semantic Scholar, OpenAlex, and Crossref & \cellcolor{Complex} Complex & 3\\
		\hline
		
		\multicolumn{4}{|l|}{\textbf{6. Testing}}\\
		\hline
		6.1 & Prepare Test Plan & \cellcolor{Medium} Medium & 1\\
		\hline
		6.2 & Design Test Cases & \cellcolor{Medium} Medium & 2\\
		\hline
		6.3 & Execute Testing & \cellcolor{Complex} Complex & 2\\
		\hline
		6.4 & Fix Defects After Testing & \cellcolor{Complex} Complex & 2\\
		\hline
		
		\multicolumn{4}{|l|}{\textbf{7. Project Finalization}}\\
		\hline
		7.1 & Complete Project Documentation & \cellcolor{Medium} Medium & 2\\
		\hline
		7.2 & Deploy the System & \cellcolor{Medium} Medium & 1\\
		\hline
		7.3 & Prepare Presentation Slides & \cellcolor{Simple} Simple & 1\\
		\hline
		
		\rowcolor{HeaderGray}
		\multicolumn{3}{|r|}{\textbf{Total Duration}} & \textbf{46 Working Days}\\
		\hline
		
	\end{longtable}
\end{document}